% ******************************* PhD Thesis Template **************************
% Please have a look at the README.md file for info on how to use the template

\documentclass[a4paper,12pt,numbered,print,index]{PhDThesisPSnPDF}

% ******************************************************************************
% ******************************* Class Options ********************************
% *********************** See README for more details **************************
%******************************************************************************

% `a4paper'(The University of Cambridge PhD thesis guidelines recommends a page
% size a4 - default option) or `a5paper': A5 Paper size is also allowed as per
% the Cambridge University Engineering Deparment guidelines for PhD thesis
%
% `11pt' or `12pt'(default): Font Size 10pt is NOT recommended by the University
% guidelines
%
% `oneside' or `twoside'(default): Printing double side (twoside) or single
% side.
%
% `print': Use `print' for print version with appropriate margins and page
% layout. Leaving the options field blank will activate Online version.
%
% `index': For index at the end of the thesis
%
% `draftclassic': For draft mode without loading any images (same as draft in book)
%
% `draft': Special draft mode with line numbers, images, and water mark with
% timestamp and custom text. Position of the text can also be modified.
%
% `abstract': To generate only the title page and abstract page with
% dissertation title and name, to submit to the Student Registry
%
% `chapter`: This option enables only the specified chapter and it's references
%  Useful for review and corrections.
%
% ************************* Custom Page Margins ********************************
%
% `custommargin`: Use `custommargin' in options to activate custom page margins,
% which can be defined in the preamble.tex. Custom margin will override
% print/online margin setup.
%
% *********************** Choosing the Fonts in Class Options ******************
%
% `times' : Times font with math support. (The Cambridge University guidelines
% recommend using times)
%
% `fourier': Utopia Font with Fourier Math font (Font has to be installed)
%            It's a free font.
%
% `customfont': Use `customfont' option in the document class and load the
% package in the preamble.tex
%
% default or leave empty: `Latin Modern' font will be loaded.
%
% ********************** Choosing the Bibliography style ***********************
%
% `authoryear': For author-year citation eg., Krishna (2013)
%
% `numbered': (Default Option) For numbered and sorted citation e.g., [1,5,2]
%
% `custombib': Define your own bibliography style in the `preamble.tex' file.
%              `\RequirePackage[square, sort, numbers, authoryear]{natbib}'.
%              This can be also used to load biblatex instead of natbib
%              (See Preamble)
%
% **************************** Choosing the Page Style *************************
%
% `default (leave empty)': For Page Numbers in Header (Left Even, Right Odd) and
% Chapter Name in Header (Right Even) and Section Name (Left Odd). Blank Footer.
%
% `PageStyleI': Chapter Name next & Page Number on Even Side (Left Even).
% Section Name & Page Number in Header on Odd Side (Right Odd). Footer is empty.
%
% `PageStyleII': Chapter Name on Even Side (Left Even) in Header. Section Number
% and Section Name in Header on Odd Side (Right Odd). Page numbering in footer

% Uncomment to change page style
%\pagestyle{PageStyleII}

% ********************************** Preamble **********************************
% Preamble: Contains packages and user-defined commands and settings
\input{Preamble/preamble}

% ************************ Thesis Information & Meta-data **********************
% Thesis title and author information, refernce file for biblatex
\input{thesis-info}

% ***************************** Abstract Separate ******************************
% To printout only the titlepage and the abstract with the PhD title and the
% author name for submission to the Student Registry, use the `abstract' option in
% the document class.

\ifdefineAbstract
 \pagestyle{empty}
 \includeonly{Declaration/declaration, Abstract/abstract}
\fi

% ***************************** Chapter Mode ***********************************
% The chapter mode allows user to only print particular chapters with references
% Title, Contents, Frontmatter are disabled by default
% Useful option to review a particular chapter or to send it to supervisior.
% To use choose `chapter' option in the document class

\ifdefineChapter
 \includeonly{Chapter3/chapter3}
\fi

% ******************************** Front Matter ********************************
\begin{document}

\frontmatter

\maketitle

\include{Dedication/dedication}
\include{Declaration/declaration}
\include{Acknowledgement/acknowledgement}
\include{Abstract/abstract}

% *********************** Adding TOC and List of Figures ***********************

\tableofcontents

\listoffigures

%\listoftables

% \printnomenclature[space] space can be set as 2em between symbol and description
%\printnomenclature[3em]

\printnomenclature

% ******************************** Main Matter *********************************
\mainmatter

\include{Chapter1/intro}
\include{Chapter2/KK_lift}
\include{Chapter3/c-proj}
\include{Chapter4/EW_and_toda}
\include{Chapter5/wormhole}





% ********************************** Back Matter *******************************
% Backmatter should be commented out, if you are using appendices after References
%\backmatter

% ********************************** Bibliography ******************************
\begin{spacing}{0.9}

% To use the conventional natbib style referencing
% Bibliography style previews: http://nodonn.tipido.net/bibstyle.php
% Reference styles: http://sites.stat.psu.edu/~surajit/present/bib.htm

\bibliographystyle{apalike}
%\bibliographystyle{unsrt} % Use for unsorted references  
%\bibliographystyle{plainnat} % use this to have URLs listed in References
\cleardoublepage
%\bibliography{References/references.bib} % Path to your References.bib file



%************************************ *************************************Temporary Bibliography *************************************



\begin{thebibliography}{}

\bibitem{AHS} 
Atiyah, M. F.  Hitchin, N. J. and  
Singer, I. M. (1978) 
 Self-duality in four-dimensional Riemannian geometry. Proc. Roy. Soc. London Ser. {\bf A 362}  425-–461

\bibitem{ADM} 
Atiyah, M., Dunajski, M. and Mason, L. (2017) Twistor theory at fifty: from contour integrals to twistor strings. 
{\tt arXiv:1704.07464}. Proceedings of the Royal Society, {\bf 473.}

%\bibitem{AWard} Atiyah, M. F. and Ward, R. S. (1977)
%Instantons and algebraic geometry. Comm. Math. Phys. {\bf 55}, 117-124

\bibitem{boyer} Boyer, C. (1988) A note on hyperhermitian four-manifolds, Proc. Amer. Math. Soc. {\bf 102},
157-164.

\bibitem{BF82} Boyer, C. and Finley, D. (1982)
Killing vectors in self‐dual, Euclidean Einstein spaces
Journal of Mathematical Physics {\bf 23}, 1126.

\bibitem{Bryant}  Bryant, R. L. (2005)
Notes on homogeneous projective surfaces.

\bibitem{BDE} Bryant, R. L., Dunajski, M. and Eastwood, M.
 (2009)  Metrisability of two-dimensional projective structures,
J. Differential Geometry {\bf 83}, 465--499.


\bibitem{Cal1} Calderbank, D. M. J. (2014)
Selfdual 4-manifolds, projective structures, and the Dunajski-West construction. SIGMA {\bf 10}, 034.

\bibitem{Cal2} Calderbank, D. M. J. (2014)
Integrable Background Geometries. SIGMA {\bf 10}, 034.

\bibitem{c_toda} Calderbank, D. M. J. (2000) The geometry of the Toda 
equation, J. Geom. Phys. {\bf 36}  152-162


\bibitem{CT} Calderbank, D. M. J. and Tod,  K. P. (2001)
Einstein metrics, hypercomplex structures and the Toda field equation
Differ. Geom. Appl. {\bf 14}  199-208.


\bibitem{osserman} Calvino-Louzao, E., Garc\' ia-R\' io, E., Gilkey, P. and Vazquez--Lorenzo, R. (2009) The geometry of modified Riemannian extensions. Proceedings of the Royal Society {\bf A465}.

\bibitem{Cartan} Cartan, E. (1940) {La geometria de las ecuationes diferenciales de tercer
orden}, Revista Mat. Hispano-Amer. {\bf 4} .


\bibitem{CDT13} Casey, S., Dunajski, M. and Tod, K. P. (2013)
Twistor geometry of a pair of second order ODEs 
Comm. Math. Phys. { \bf 321}, 681--701.



\bibitem{ALHref} Cherkis, S. A.  and Kapustin, A. (1999) Singular monopoles and gravitational
instantons, Comm. Math. Phys. {\bf 203} , 713–728.


\bibitem{Doubrov} 
Doubrov, B. (2008) Generalized Wilczynski invariants for non-linear ordinary differential equations.
The IMA Volumes in Mathematics and its Applications {\bf 144}, 25-40.

\bibitem{DM} Dunajski, M and Mettler, T. (2017) Gauge theory on projective surfaces and anti-self-dual Einstein metrics in dimension four.  
 J. Geom Anal 1--32. {\it{arXiv:1509.04276}}.
 

\bibitem{DGW} Dunajski M., Gover, A. R. and Waterhouse, A. (2018) Some examples of projective and c-projective compactifications of Einstein metrics  {\tt arXiv:1807.06105}.

\bibitem{D99} Dunajski, M. (1999) The twisted photon associated to hyper-Hermitian four-manifolds. J. Geom. Phys. {\bf 30}, 266--281

\bibitem{MDbook} Dunajski, M. Solitons, Instantons, and Twistors, {\em Oxford Graduate Texts in Mathematics}, Oxford University Press, 2009.

\bibitem{FLL} Falla Luza, H. M. and Loray, F. (2017)  Projective structures and neighbourhoods of rational curves.

\bibitem{FP} Finley, J.D. and Pleba\'nski, J.F. (1979) The classification of all H spaces admitting a Killing
vector, J. Math. Phys. {\bf 20}, 1938.

\bibitem{F}  Ferapontov, E.  V., Korotkin D. A.  and Shramchenko, V. A. (2002)
Boyer–Finley equation and systems of hydrodynamic type.
Classical and Quantum Gravity, {\bf 19}.

\bibitem{GH} Gibbons, G. W. and Hawking, S. W. (1979) Classification of Gravitational Instanton Symmetries.
Comm. Math. Phys. {\bf 66}, 291--310.

\bibitem{Gibbons:1979zt}
Gibbons, G. W. and Hawking, S. W. (1978)
Gravitational Multi - Instantons.
Phys. Lett. \textbf{B78}
430.

\bibitem{Gibbons:1998ie}
Gibbons, G. W. and Rychenkova, P. (2000)
Single-sided domain walls in M-theory.
J. Geom. Phys. \textbf{32}. 311-340.

\bibitem{Grossman} Grossman, D. (2000) Torsion-free path geometries and integrable second order ODE systems, Selecta
Math. (N.S.) 6, 399-442.

\bibitem{hitchin} Hitchin, N. J. (1982) in {\em Twistor Geometry and Non-linear Systems}, Lecture Notes in Mathematics vol {\bf 970} Berlin: Springer

\bibitem{JT} 
Jones, P. E. and  Tod, K. P (1985)
Minitwistor spaces and Einstein-Weyl spaces. 
Classical Quantum Gravity {\bf 15}, 565--577.

\bibitem{Kob}
Kobayashi, S. (1963)
Topology of positively pinched K\"ahler manifolds.
Tohoku Math. J. {\bf 2}, 121--139

\bibitem{LeBrun} LeBrun, C. (1991)
Explicit self--dual metrics on $\mathbb{CP}_2\#\dots \#\mathbb{CP}_2$
J. Diff. Geom {\bf 34}, 223--253

\bibitem{MS} Manakov, S. V. and Santini, P. M. (2009)
The dispersionless 2D Toda equation: dressing, Cauchy problem, longtime behaviour, implicit solutions and wave breaking. J. Phys. {\bf A42}.

\bibitem{martina} 
Martina, L. Sheftel, M. and Winternitz, P.(2001)
Group foliation and non-invariant
solutions of the heavenly equation.
J. Phys. {\bf A34}.

\bibitem{MW} Mason, L. J. and Woodhouse, N. M. J.  Integrability, self-duality and twistor theory, {\em London Mathematical Society Monographs. New Series}, Vol. 15, The Clarendon Press, Oxford University Press, New York, 1996.


\bibitem{PT} Pedersen, H. and Tod, P. (1993)
Three-Dimensional Einstein-Weyl Geometry,
Advances in Mathematics, {\bf 97}, 74-109


\bibitem{penrose} Penrose, R. (1976) Nonlinear 
gravitons and curved twistor theory, Gen. Rel. Grav.  {\bf 7},  31--52

\bibitem{Pope} Pope, C. Kaluza--Klein Theory.

\bibitem{prim} Plansangkate, P. (2018)
Skyrm fields, multi-instantons and $SU(\infty)$-Toda equation.
Nonlinearity {\bf 32}, 88.
{\tt arXiv:1611.01444.}

\bibitem{Prz} Przanowski, M. (1991)
Killing vector fields in self--dual, Euclidean Einstein spaces with $\Lambda\neq 0$,
J. Math. Phys. {\bf 32}, 1004-1010

\bibitem{Sheftel} Sheftel, M. (2003)
Method of group foliation, hodograph transformation and non-invariant solutions of the Boyer-Finley equation.
{\tt arXiv: 0305040}.

\bibitem{Tod_toda} Tod, P. (1995)
Scalar--flat K\"ahler and hyper--K\"ahler metrics from Painlev\'e --III,
Class. Quantum Grav. {\bf 12} 1535-1547

\bibitem{Tod_toda2} Tod, P. (1997)
The $SU(\infty)$--Toda field equation and special four--dimensional metrics,
in {\em Geometry and Physics} (Aarhus, 1995), Lecture Notes in Pure and Applied Mathematics {\bf 184}, 307-312 Dekker, New York.

\bibitem{Tod_note} Tod, P. (2006) {A note on Riemannian anti--self--dual Einstein metrics with symmetry}

\bibitem{T} Tod, P. (2000) {Einstein-Weyl spaces and third-order differential equations}, J. Math. Phys. {\bf 41}.



\bibitem{wardtf} Ward, R. S. (1976)
The Twisted Photon,
Twistor Newsletter {\bf 1}, 7-8

\bibitem{ward} Ward, R. S. (1977)
On Self--Dual Gauge Fields,
Phys. Lett. A {\bf 61}, 81--82

\bibitem{ward}   Ward, R. S. (1980)
Self-dual space-times with cosmological constant,
Comm. Math. Phys. {\bf 78},  1-17.

\bibitem{ward_toda} Ward, R. S. (1990) Einstein-Weyl spaces and 
$SU(\infty)$ Toda fields. Classical Quantum Gravity {\bf 7} (1990), L95–L98.


\bibitem{West} West, S. (2007) {\em Neutral ASD Conformal Structures with Null Killing Vectors.} Thesis. University of Cambridge.

\bibitem{yano} Yano, K. {\em The Theory Of Lie Derivatives And Its Applications.} North Holland, Amsterdam, 1955.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\bibitem{BEG} Bailey, T. N., Eastwood M. G., Gover, A. R., (1994)
Thomas's structure bundle for conformal, projective
  and related structures, {\em Rocky Mountain Journal of
    Mathematics}, {\bf 24}, 1--27.
  
\bibitem{bar} Bar, C. (1993) 
Real Killing Spinors and Holonomy,
Comm. Math. Phys. {\bf 154}, 509-521.

\bibitem{bryant_exeptional} Bryant, R. L. (1987)
Metrics with exceptional holonomy. Ann. Math. {\bf 126}, 525-576.


\bibitem{CG0} \v Cap, A. and Gover, A. R. (2016)
Projective Compactifications and Einstein metrics.
J. Reine Angew. Math. {\bf 717.}  47-75

\bibitem{CG} \v Cap, A. and Gover, A. R. (2016)
C-Projective Compactification; (quasi--)Kaehler Metrics and CR boundaries.
{\em  American Journal of Mathematics}, in press. \quad   {\it arXiv:1603.07039}.

\bibitem{CGH-duke} \v Cap, A., Gover, A. R., Hammerl, M., (2014) 
  Holonomy reductions of Cartan geometries and curved orbit
  decompositions, {\em Duke Mathematical Journal}. 
{\bf 163}, no. 5, 1035--1070.
 \quad arXiv:1103.4497

  
\bibitem{CS-book} 
\v{C}ap, A. and Slov\'ak, J. (2009)
\emph{Parabolic Geometries I: Background and General Theory},
American Mathematical Society 2009.


\bibitem{c_proj} Calderbank,  D. M. J.,  Eastwood, M. G.,  Matveev, V. S. and 
Neusser, K.  (2016) C-projective geometry. {\tt arXiv:1512.04516}






\bibitem{EH} 
Eguchi, T. and Hanson, A. J. (1978) Asymptotically flat self--dual solutions
to Euclidean gravity, Phys. Lett. B74, 249-251.

\bibitem{gray} 
Gray, A. and Hervella, L. M. (1980) The sixteen classes of almost Hermitian manifolds and their linear
invariants. Ann. Mat. Pura Appl. {\bf 123}, 35-58.

\bibitem{Lieb}
Libermann, P. (1954) Sur le probleme d'equivalence de certaines structures infinitesimales, Ann.
Mat. Pura Appl. {\bf 36}, 27???120.


\bibitem{LC} Levi--Civita, T. (1896) On the transformations of the 
dynamical equations. Annali di Mathematica, {\bf 24}, 255-300.

\bibitem{matveev} Matveev, V. S. and Rosemann, S. (2015)
The degree of mobility of Einstein metrics.
{\tt arXiv:1503.00968.}


\bibitem{melrose}
Melrose, R. B. (1995)
{\em Geometric scattering theory.} Stanford Lectures. Cambridge University Press,
Cambridge.

\bibitem{penrose65}
Penrose. R. (1965) Zero rest-mass fields including gravitation: asymptotic behaviour, Proc. R. 
Soc. London, Ser. {\bf A284}, 159-203.

\bibitem{uhlen} Uhlenbeck, K. (1982) Removable singularities in Yang-Mills fields,
Commun. Math. Phys. {\bf 83}, 11--29.

\bibitem{witten} Witten, E. (1998)
Anti de Sitter space and holography. Adv. Theor. Math. Phys. {\bf 2}, 253--291.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{wavemaps} Bizo\'n, P. and Kahl, M. (2015)
Wave maps on a wormhole. Phys. Rev. D {\bf 91} 065003

\bibitem{SG} Bizo\'n, P., Dunajski, M., Gibbons, G., Kahl, M. and Kowalczyk, M. (2018) Sine-Gordon on a Wormhole (upcoming).

\bibitem{Bronnikov} Bronnikov, K. A. (1973)
Scalar--tensor theory and scalar charge. Acta Phys. Polonica {\bf b4} 251--266

\bibitem{Ellis} Ellis, H. G. (1973)
Ether flow through a drainhole: A particle model in general relativity. J. Math. Phys. {\bf 14}, 104--118

\bibitem{Hall} Hall, B. C. (2013)
Quantum Theory for Mathematicians. Graduate Texts in Mathematics {\bf 267}, Springer

\bibitem{KowalczykMM} Kowalczyk, M., Martel, Y. and Mu\~noz, C.
Kink Dynamics in the $\phi^4$ Model: Asymptotic Stability for Odd Perturbations in the Energy Space. 

\bibitem{Manton&Merabet} Manton, N. S. and Merabet, H. (1997)
$\phi^4$ Kinks - Gradient Flow and Dynamics. Nonlinearity {\bf 10} 3--18

\bibitem{Manton&Sutcliffe} Manton, N. S. and Sutcliffe, P. (2004)
Topological Solitons. Cambridge Monographs on Mathematical Physical, Cambridge University Press, Cambridge

\bibitem{Segur} Segur, H. (1983)
Wobbling kinks in $\varphi^4$ and sine-Gordon theory. Journal of Mathematical Physics {\bf 24}, 1439--1444

\bibitem{SW98} Soffer, A. and Weinstein, M. I. (1998)
Time Dependent Resonance Theory. Geometric and Functional Analysis {\bf 8} 1086--1128

\bibitem{SW99} Soffer, A. and Weinstein, M. I. (1999)
Resonances, radiation damping and instability in Hamiltonian nonlinear wave equations. Invent. math. {\bf 136} 9--74

\bibitem{TT} Tao, T. (2009)
Why are Solitons Stable? American Mathematical Society {\bf 46} 1-33

\bibitem{Weinstein} (2002)
Extended Hamiltonian Systems. Handbook of Dynamical Systems IB, 1135--1153

\bibitem{XinliangSoffer} Xinliang, An. and Soffer, A. (2017)
Fermi's golden rule and $H^1$ scattering for nonlinear Klein--Gordon equations with metastable states

\bibitem{hyp_foliations} Zenginoglu, A. (2008)
Hyperboloidal foliations and scri-fixing. Class. Quant. Grav. {\bf 25} 145002

\bibitem{sym_hyp} Zenginoglu, A. (2008)
A hyperboloidal study of tail decay rates for scalar and Yang-Mills fields. Class. Quant. Grav. {\bf 25} 175013




%\bibitem{SW03} Soffer, A. and Weinstein, M. I. (2003)
%Selection of the Ground State for Nonlinear Schr\"odinger Equations.
%Rev. Math. Phys. {\bf 16} 977--1071


\end{thebibliography}

% If you would like to use BibLaTeX for your references, pass `custombib' as
% an option in the document class. The location of 'reference.bib' should be
% specified in the preamble.tex file in the custombib section.
% Comment out the lines related to natbib above and uncomment the following line.

%\printbibliography[heading=bibintoc, title={References}]


\end{spacing}

% ********************************** Appendices ********************************

%\begin{appendices} % Using appendices environment for more functunality

%%\include{Appendix2/appendix2}

%\end{appendices}

% *************************************** Index ********************************
\printthesisindex % If index is present

\end{document}
