
\begin{thebibliography}{}

\bibitem{Eastwood} Eastwood, M. (2008)
Notes on Projective Differential Geometry.

\bibitem{Cartan} Cartan, E. (1924)
Sur les vari\'et\'es a connexion projective.
\textit{Bull. Soc. Math. France} {\bf 52}, 205--241.

\bibitem{Klein} Klein, F. (1872)
Vergleichende Betrachtungen \"uber neuere geometrische Forschungen. \textit{Math. Ann.} {\bf 43}, 63--100.

\bibitem{KobNag} Kobayashi, S. and Nagano, T. (1964)
On projective connections. \textit{J. Math. Mech.} {\bf 13}, 215--235.

\bibitem{Sharpe} Sharpe, R. W.
\textit{Differential Geometry: Cartan's Generalization of Klein's Erlangen Program.} Springer, New York, 1997.

\bibitem{arnold}
Arnold, V. I.
\textit{Mathematical Methods of Classical Mechanics.} Springer, 1989.

\bibitem{AHS} 
Atiyah, M. F.  Hitchin, N. J. and  Singer, I. M. (1978) 
Self-duality in four-dimensional Riemannian geometry. \textit{Proc. Roy. Soc. London Ser.} {\bf A 362},  425--461.

\bibitem{ADM} 
Atiyah, M., Dunajski, M. and Mason, L. (2017)
Twistor theory at fifty: from contour integrals to twistor strings. \textit{Proc. Roy. Soc.} {\bf 473.}

%\bibitem{AWard} Atiyah, M. F. and Ward, R. S. (1977)
%Instantons and algebraic geometry. Comm. Math. Phys. {\bf 55}, 117-124

\bibitem{boyer} Boyer, C. (1988)
A note on hyperhermitian four-manifolds \textit{Proc. Amer. Math. Soc.} {\bf 102},
157--164.

\bibitem{BF82} Boyer, C. and Finley, D. (1982)
Killing vectors in self‐-dual, Euclidean Einstein spaces. \textit{J. Math. Phys.} {\bf 23}, 1126.

\bibitem{Bryant}  Bryant, R. L. (2005)
Notes on homogeneous projective surfaces.

\bibitem{BDE} Bryant, R. L., Dunajski, M. and Eastwood, M. (2009)
Metrisability of two-dimensional projective structures.
J. Differ. Geom. {\bf 83}, 465--499.


\bibitem{Cal1} Calderbank, D. M. J. (2014)
Selfdual 4-manifolds, projective structures, and the Dunajski-West construction. SIGMA {\bf 10}, 035.

\bibitem{Cal2} Calderbank, D. M. J. (2014)
Integrable Background Geometries. SIGMA {\bf 10}, 034.

\bibitem{c_toda} Calderbank, D. M. J. (2000) The geometry of the Toda 
equation. \textit{J. Geom. Phys.} {\bf 36},  152--162.


\bibitem{CT} Calderbank, D. M. J. and Tod,  K. P. (2001)
Einstein metrics, hypercomplex structures and the Toda field equation.
\textit{Differ. Geom. Appl.} {\bf 14},  199--208.


\bibitem{osserman} Calvino-Louzao, E., Garc\' ia-R\' io, E., Gilkey, P. and Vazquez--Lorenzo, R. (2009) The geometry of modified Riemannian extensions. \textit{Proc. Roy. Soc.} {\bf A465}, 2107

%\bibitem{Cartan3} Cartan, E. (1940) {La geometria de las ecuationes diferenciales de tercer
%orden}. \textit{Revista Mat. Hispano-Amer.} {\bf 4} .


\bibitem{CDT13} Casey, S., Dunajski, M. and Tod, K. P. (2013)
Twistor geometry of a pair of second order ODEs. 
\textit{Comm. Math. Phys.} { \bf 321}, 681--701.



\bibitem{ALHref} Cherkis, S. A.  and Kapustin, A. (1999) Singular monopoles and gravitational
instantons. \textit{Comm. Math. Phys.} {\bf 203}, 713--728.


%\bibitem{Doubrov} 
%Doubrov, B. (2008) Generalized Wilczynski invariants for non-linear ordinary differential equations.
%The IMA Volumes in Mathematics and its Applications {\bf 144}, 25-40.

\bibitem{DM} Dunajski, M. and Mettler, T. (2018) Gauge theory on Projective Surfaces and Anti-self-dual Einstein Metrics in Dimension Four.  
\textit{J. Geom. Anal.} {\bf 28}, 2780--2811.
 
\bibitem{DW} Dunajski, M. and Waterhouse, A. (2019)
Einstein Metrics, Projective Structures and the $SU(\infty)$ Toda Equation.
{\tt{arXiv:1509.04276}}
 

\bibitem{DGW} Dunajski M., Gover, A. R. and Waterhouse, A. (2018) Some examples of projective and c-projective compactifications of Einstein metrics.  {\tt arXiv:1807.06105}

\bibitem{DT} Dunajski, M. and Tod, K. P. (2010) Four Dimensional Metrics Conformal to K\"ahler. \textit{Math. Proc. Camb. Phil. Soc.} {\bf 148}, 485--503.

\bibitem{D99} Dunajski, M. (1999) The twisted photon associated to hyper-Hermitian four-manifolds. \textit{J. Geom. Phys.} {\bf 30}, 266--281.

\bibitem{MDbook} Dunajski, M. \textit{Solitons, Instantons, and Twistors.} Oxford Graduate Texts in Mathematics, Oxford University Press, 2009.

\bibitem{DFK} Dunajski, M., Ferapontov, E. and Kruglikov, B. (2015)
On the Einstein--Weyl and conformal self--duality equations. \textit{J. Math. Phys.} {\bf 56}, 8.

\bibitem{FLL} Falla Luza, H. M. and Loray, F. (2017)  Projective structures and neighbourhoods of rational curves.

\bibitem{FP} Finley, J.D. and Pleba\'nski, J.F. (1979) The classification of all H spaces admitting a Killing
vector. \textit{J. Math. Phys.} {\bf 20}, 1938.

\bibitem{F}  Ferapontov, E.  V., Korotkin D. A.  and Shramchenko, V. A. (2002)
Boyer–Finley equation and systems of hydrodynamic type.
\textit{Class. Quantum Gravity} {\bf 19}, 24.

\bibitem{GH} Gibbons, G. W. and Hawking, S. W. (1979) Classification of Gravitational Instanton Symmetries.
\textit{Comm. Math. Phys.} {\bf 66}, 291--310.

\bibitem{Gibbons:1979zt}
Gibbons, G. W. and Hawking, S. W. (1978)
Gravitational Multi - Instantons.
\textit{Phys. Lett.} \textbf{B78},
430.

%\bibitem{Gibbons:1998ie}
%Gibbons, G. W. and Rychenkova, P. (2000)
%Single-sided domain walls in M-theory.
%J. Geom. Phys. \textbf{32}. 311-340.

\bibitem{Grossman} Grossman, D. (2000) Torsion-free path geometries and integrable second order ODE systems. \textit{Selecta
Math. (N.S.)} {\bf 6}, 399--442.

\bibitem{hitchin} Hitchin, N. J. (1982) in {\em Twistor Geometry and Non-linear Systems}, Lecture Notes in Mathematics vol {\bf 970} Berlin: Springer

\bibitem{JT} 
Jones, P. E. and  Tod, K. P (1985)
Minitwistor spaces and Einstein-Weyl spaces. 
\textit{Class. Quantum Gravity} {\bf 15}, 565--577.

\bibitem{Kob}
Kobayashi, S. (1963)
Topology of positively pinched K\"ahler manifolds.
\textit{Tohoku Math. J.} {\bf 2}, 121--139.

\bibitem{Kodaira} Kodaira, K.(1963)
On stability of compact submanifolds of complex manifolds.
\textit{Am. J. Math.} {\bf 85}, 79--94.

\bibitem{LeBrun} LeBrun, C. (1991)
Explicit self--dual metrics on $\mathbb{CP}_2\#\dots \#\mathbb{CP}_2$.
\textit{J. Differ. Geom} {\bf 34}, 223--253.

\bibitem{LeBrun83} LeBrun, C. (1983)
Spaces of Complex Null Geodesics in Complex--Riemannian geometry. \textit{Trans. Am. Math. Soc.} {\bf 278}, 209--231.

\bibitem{MS} Manakov, S. V. and Santini, P. M. (2009)
The dispersionless 2D Toda equation: dressing, Cauchy problem, longtime behaviour, implicit solutions and wave breaking. \textit{J. Phys.} {\bf A42}.

\bibitem{martina} 
Martina, L. Sheftel, M. and Winternitz, P.(2001)
Group foliation and non-invariant
solutions of the heavenly equation.
\textit{J. Phys.} {\bf A34}.

\bibitem{MW} Mason, L. J. and Woodhouse, N. M. J.  \textit{Integrability, self-duality and twistor theory.} London Mathematical Society Monographs, New Series, Vol. 15, The Clarendon Press, Oxford University Press, New York, 1996.

\bibitem{complex_mfds} Morrow, J. and Kodaira, K. (2006)
\textit{Complex Manifolds.} AMS bookstore, Providence, RI.

\bibitem{PT} Pedersen, H. and Tod, P. (1993)
Three-Dimensional Einstein-Weyl Geometry,
\textit{Adv. Math.} {\bf 97}, 74--109.


\bibitem{penrose} Penrose, R. (1976) Nonlinear 
gravitons and curved twistor theory. \textit{Gen. Rel. Grav.}  {\bf 7},  31--52.

\bibitem{penroserindler} Penrose, R. and Rindler, W.
\textit{Spinors and Spacetime, Volumes I and II.} Cambridge University Press 1984.

\bibitem{Pope} Pope, C. Kaluza--Klein Theory.

%\bibitem{prim} Plansangkate, P. (2018)
%Skyrm fields, multi-instantons and $SU(\infty)$-Toda equation.
%Nonlinearity {\bf 32}, 88.
%{\tt arXiv:1611.01444.}

\bibitem{Prz} Przanowski, M. (1991)
Killing vector fields in self--dual, Euclidean Einstein spaces with $\Lambda\neq 0$.
\textit{J. Math. Phys.} {\bf 32}, 1004--1010.

\bibitem{Sheftel} Sheftel, M. (2003)
Method of group foliation, hodograph transformation and non-invariant solutions of the Boyer-Finley equation.
{\tt arXiv: 0305040}

\bibitem{Tod_toda} Tod, P. (1995)
Scalar--flat K\"ahler and hyper--K\"ahler metrics from Painlev\'e --III.
\textit{Class. Quantum Grav.} {\bf 12}, 1535--1547.

\bibitem{Tod_toda2} Tod, P. (1997)
The $SU(\infty)$--Toda field equation and special four--dimensional metrics,
in {\em Geometry and Physics} (Aarhus, 1995), Lecture Notes in Pure and Applied Mathematics {\bf 184}, 307--312 Dekker, New York.

\bibitem{Tod_note} Tod, P. (2006) {A note on Riemannian anti--self--dual Einstein metrics with symmetry}

%\bibitem{T} Tod, P. (2000) {Einstein-Weyl spaces and third-order differential equations}, J. Math. Phys. {\bf 41}.



\bibitem{wardtf} Ward, R. S. (1976)
The Twisted Photon.
\textit{Twistor Newsletter} {\bf 1}, 7--8.

\bibitem{wardGauge} Ward, R. S. (1977)
On Self--Dual Gauge Fields.
\textit{Phys. Lett. A} {\bf 61}, 81--82.

\bibitem{ward}   Ward, R. S. (1980)
Self--dual space--times with cosmological constant,
\textit{Comm. Math. Phys.} {\bf 78},  1--17.

\bibitem{ward_toda} Ward, R. S. (1990) Einstein-Weyl spaces and 
$SU(\infty)$ Toda fields. \textit{Class. Quantum Gravity} {\bf 7}, L95--L98.


\bibitem{West} West, S. {\em Neutral ASD Conformal Structures with Null Killing Vectors.} Thesis. University of Cambridge, 2007.

\bibitem{yano} Yano, K. {\em The Theory Of Lie Derivatives And Its Applications.} North Holland, Amsterdam, 1955.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\bibitem{BEG} Bailey, T. N., Eastwood M. G. and Gover, A. R. (1994)
Thomas's structure bundle for conformal, projective
  and related structures. {\em Rocky Mt. J.
    Math.} {\bf 24}, 1--27.
  
%\bibitem{bar} Bar, C. (1993) 
%Real Killing Spinors and Holonomy,
%Comm. Math. Phys. {\bf 154}, 509-521.

%\bibitem{bryant_exeptional} Bryant, R. L. (1987)
%Metrics with exceptional holonomy. Ann. Math. {\bf 126}, 525-576.


\bibitem{CG0} \v Cap, A. and Gover, A. R. (2016)
Projective Compactifications and Einstein metrics.
\textit{J. Reine Angew. Math.} {\bf 717},  47--75.

\bibitem{CG} \v Cap, A. and Gover, A. R. (2016)
C-Projective Compactification; (quasi--)Kaehler Metrics and CR boundaries.
{\em  Am. J. Math.} {\bf 141}.

\bibitem{CGH-duke} \v Cap, A., Gover, A. R. and Hammerl, M. (2014) 
  Holonomy reductions of Cartan geometries and curved orbit
  decompositions. {\em Duke Math. J.} 
{\bf 163}, 1035--1070.
 
  
%\bibitem{CS-book} 
%\v{C}ap, A. and Slov\'ak, J. (2009)
%\emph{Parabolic Geometries I: Background and General Theory},
%American Mathematical Society 2009.


\bibitem{c_proj} Calderbank,  D. M. J.,  Eastwood, M. G.,  Matveev, V. S. and 
Neusser, K.  (2016) C-projective geometry. {\tt arXiv:1512.04516}


%\bibitem{gray} 
%Gray, A. and Hervella, L. M. (1980) The sixteen classes of almost Hermitian manifolds and their linear
%invariants. Ann. Mat. Pura Appl. {\bf 123}, 35-58.

\bibitem{Lieb}
Libermann, P. (1954) Sur le probleme d'equivalence de certaines structures infinitesimales. \textit{Ann.
Mat. Pura Appl.} {\bf 36}, 27--120.


\bibitem{LC} Levi--Civita, T. (1896) On the transformations of the 
dynamical equations. \textit{Ann. Mat. Pura Appl.} {\bf 24}, 255--300.

\bibitem{matveev} Matveev, V. S. and Rosemann, S. (2015)
The degree of mobility of Einstein metrics. \textit{J. Geom. Phys.}
{\bf 99}, 42--56.


\bibitem{melrose}
Melrose, R. B. (1995)
{\em Geometric scattering theory.} Stanford Lectures. Cambridge University Press,
Cambridge.

\bibitem{penrose65}
Penrose. R. (1965) Zero rest-mass fields including gravitation: asymptotic behaviour. \textit{Proc. R. 
Soc. London, Ser.} {\bf A284}, 159--203.

\bibitem{uhlen} Uhlenbeck, K. (1982) Removable singularities in Yang-Mills fields.
\textit{Commun. Math. Phys.} {\bf 83}, 11--29.

\bibitem{witten} Witten, E. (1998)
Anti de Sitter space and holography. \textit{Adv. Theor. Math. Phys.} {\bf 2}, 253--291.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibitem{me} Waterhouse, A. (2019)
The $\phi^4$ kink on a wormhole spacetime. {\tt arXiv: 1908.09650}

\bibitem{wavemaps} Bizo\'n, P. and Kahl, M. (2015)
Wave maps on a wormhole. \textit{Phys. Rev. D} {\bf 91}, 065003

\bibitem{SG} Bizo\'n, P., Dunajski, M., Gibbons, G., Kahl, M. and Kowalczyk, M. (2018) Sine-Gordon on a Wormhole (preprint).

\bibitem{Bronnikov} Bronnikov, K. A. (1973)
Scalar--tensor theory and scalar charge. \textit{Acta Phys.} Polonica {\bf b4}, 251--266

\bibitem{Ellis} Ellis, H. G. (1973)
Ether flow through a drainhole: A particle model in general relativity. \textit{J. Math. Phys.} {\bf 14}, 104--118.

%\bibitem{Hall} Hall, B. C. (2013)
%Quantum Theory for Mathematicians. Graduate Texts in Mathematics {\bf 267}, Springer

\bibitem{KowalczykMM} Kowalczyk, M., Martel, Y. and Mu\~noz, C. (2017)
Kink Dynamics in the $\phi^4$ Model: Asymptotic Stability for Odd Perturbations in the Energy Space.\textit{J. Amer. Math. Soc.} {\bf 30}, 769--798.

\bibitem{Manton&Merabet} Manton, N. S. and Merabet, H. (1997)
$\phi^4$ Kinks - Gradient Flow and Dynamics. \textit{Nonlinearity} {\bf 10}, 3--18.

\bibitem{Manton&Sutcliffe} Manton, N. S. and Sutcliffe, P. (2004)
\textit{Topological Solitons.} Cambridge Monographs on Mathematical Physical, Cambridge University Press, Cambridge.

\bibitem{BarrySimon} Simon, B. (1975)
The Bound State of Weakly Coupled Schr\"odinger Operators in One and Two Dimensions. \textit{Ann. Phys.} {\bf 97}, 279--288.

%\bibitem{Segur} Segur, H. (1983)
%Wobbling kinks in $\varphi^4$ and sine-Gordon theory. Journal of Mathematical Physics {\bf 24}, 1439--1444

\bibitem{SW98} Soffer, A. and Weinstein, M. I. (1998)
Time Dependent Resonance Theory. \textit{Geom. Funct. Anal.} {\bf 8}, 1086--1128.

\bibitem{SW99} Soffer, A. and Weinstein, M. I. (1999)
Resonances, radiation damping and instability in Hamiltonian nonlinear wave equations. \textit{Invent. math.} {\bf 136}, 9--74.

\bibitem{TT} Tao, T. (2009)
Why are Solitons Stable? \textit{Am. Math. Soc.} {\bf 46}, 1--33.

\bibitem{Weinstein} (2002)
Extended Hamiltonian Systems. \textit{Handbook of Dynamical Systems} IB, 1135--1153.

\bibitem{XinliangSoffer} Xinliang, An. and Soffer, A. (2017)
Fermi's golden rule and $H^1$ scattering for nonlinear Klein--Gordon equations with metastable states.

\bibitem{hyp_foliations} Zenginoglu, A. (2008)
Hyperboloidal foliations and scri-fixing. \textit{Class. Quantum Gravity} {\bf 25}, 145002.

\bibitem{sym_hyp} Zenginoglu, A. (2008)
A hyperboloidal study of tail decay rates for scalar and Yang-Mills fields. \textit{Class. Quantum Gravity} {\bf 25}, 175013.




%\bibitem{SW03} Soffer, A. and Weinstein, M. I. (2003)
%Selection of the Ground State for Nonlinear Schr\"odinger Equations.
%Rev. Math. Phys. {\bf 16} 977--1071

\end{thebibliography}